Output Summary

### 2021-08-03 03-post-process/output-plots.Rmd
Introduce a new framework for easily accessing specific posterior summaries
The indexing in the model gets quite complex in some areas. Take returns to the estuary by year, age, sex, origin, and population: Rb[y,k,s,o,j]. If we wish to extract the posterior summary of all age 4 natural origin males for UGR, we would write: post_summ(post, "Rb[.+,2,2,1,4]"). This is confusing to read and edit when copying and pasting to summarize a similar quantity but for a different combo of age/sex/origin/population.

This commit introduces the function `sub_index()`, which makes this task much easier. Coupl

>>>>

```{r dimension-ids}
# population names
pops = colnames(jags_data$Ra_obs)

# dimension IDs
i_fall   = 1  # fall migrants are i = 1
i_spring = 2  # spring migrants are i = 2,
o_nor    = 1  # natural origin are o = 1,
o_hor    = 2  # hatchery origin are o = 2,
s_female = 1  # females are s = 1,
s_male   = 2  # males are s = 2
j_cat    = 1  # Catherine Creek is j = 1
j_los    = 2  # Lostine River is j = 2
j_min    = 3  # Minam River is j = 3
j_ugr    = 4  # Upper Grande Ronde River is j = 4
k_3      = 1  # age 3 is k = 1
k_4      = 2  # age 4 is k = 2
k_5      = 3  # age 5 is k = 3
```
